Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-14 paper_comparison/appendix.Rmd
update analysis for alpha

The analysis is conducted by setting up two relatively extreme scenarios, where the $\alpha$ is under or overestimated by 25%. Using the inflated and deflated $\hat{\alpha}$, we recalculate the $p$-value for every lineup and show the results in Figure \ref{fig:sensitive}. It can be observed that $p$-value changes very little. It is very unlikely the findings will be affected because of the estimate of $\alpha$.

```{r}
vi_survey_upper <- calc_p_value_multi(vi_survey %>%
                                        mutate(alpha_upper = alpha * 1.25,
                                               alpha_lower = alpha * 0.75),
                                      lineup_id = unique_lineup_id,
                                      detect = detect,
                                      n_sel = num_selection,
                                      alpha = alpha_upper) %>%
  right_join(select(vi_survey, -p_value))

vi_survey_lower <- calc_p_value_multi(vi_survey %>%
                                        mutate(alpha_upper = alpha * 1.25,
                                               alpha_lower = alpha * 0.75),
                                      lineup_id = unique_lineup_id,
                                      detect = detect,
                                      n_sel = num_selection,
                                      alpha = alpha_lower) %>%
  right_join(select(vi_survey, -p_value))
```

@@

```{r sensitive, fig.cap = "\\label{fig:sensitive}Change of $p$-values with $\\hat{\\alpha}$ inflated by 25% and deflated by 25%."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value)) %>%
  left_join(
vi_survey_upper %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_upper = first(p_value))) %>%
  left_join(
vi_survey_lower %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_lower = first(p_value))) %>%
  pivot_longer(p_value_upper:p_value_lower) %>%
  mutate(name = ifelse(name == "p_value_upper", "+25%", "-25%")) %>%
  ggplot() +
  geom_point(aes(p_value, value), alpha = 0.2) +
  geom_abline() +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~name) +
  ylab("Adjusted p-value") +
  xlab("p-value") +
  coord_fixed()
```

@@

>>>>

The analysis is conducted by setting up two relatively extreme scenarios, where the $\alpha$ is under or overestimated by 50%. Using the inflated and deflated $\hat{\alpha}$, we recalculate the $p$-value for every lineup and show the results in Figure \ref{fig:sensitive}. It can be observed that there are some changes to $p$-values, especially when the $\hat{\alpha}$ is deflated. However, Figure \ref{fig:sensitive-barplot} shows that adjusting $\hat{\alpha}$ will not result in a huge difference in rejection decisions. There are only a small number of cases (12 out of 558) where the rejection decision changes. It is very unlikely the downstream findings will be affected because of the estimate of $\alpha$.

```{r}
vi_survey_upper <- calc_p_value_multi(vi_survey %>%
                                        mutate(alpha_upper = alpha * 1.5,
                                               alpha_lower = alpha * 0.5),
                                      lineup_id = unique_lineup_id,
                                      detect = detect,
                                      n_sel = num_selection,
                                      alpha = alpha_upper) %>%
  right_join(select(vi_survey, -p_value))

vi_survey_lower <- calc_p_value_multi(vi_survey %>%
                                        mutate(alpha_upper = alpha * 1.5,
                                               alpha_lower = alpha * 0.5),
                                      lineup_id = unique_lineup_id,
                                      detect = detect,
                                      n_sel = num_selection,
                                      alpha = alpha_lower) %>%
  right_join(select(vi_survey, -p_value))
```

@@

```{r sensitive, fig.cap = "\\label{fig:sensitive}Change of $p$-values with $\\hat{\\alpha}$ inflated by 50% and deflated by 50%."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value)) %>%
  left_join(
vi_survey_upper %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_upper = first(p_value))) %>%
  left_join(
vi_survey_lower %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_lower = first(p_value))) %>%
  pivot_longer(p_value_upper:p_value_lower) %>%
  mutate(name = ifelse(name == "p_value_upper", "+50%", "-50%")) %>%
  ggplot() +
  geom_point(aes(p_value, value), alpha = 0.2) +
  geom_abline() +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~name) +
  ylab("Adjusted p-value") +
  xlab("p-value") +
  coord_fixed() +
  theme_light()
```

```{r sensitive-barplot, fig.cap = "\\label{fig:sensitive-barplot}Change of rejection of the null hypothesis with $\\hat{\\alpha}$ inflated by 50% and deflated by 50%."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value)) %>%
  left_join(
vi_survey_upper %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_upper = first(p_value))) %>%
  left_join(
vi_survey_lower %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_lower = first(p_value))) %>%
  pivot_longer(p_value_upper:p_value_lower) %>%
  mutate(name = ifelse(name == "p_value_upper", "+50%", "-50%")) %>%
  ggplot() +
  geom_bar(aes(p_value < 0.05, fill = value < 0.05), position = "dodge") +
  theme_light() +
  xlab("p-value < 0.05") +
  labs(fill = "Adjusted p-value < 0.05")
```

@@

\newpage

## References
